---
output: rmarkdown::github_document
---
```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, collapse = TRUE)
```
# homebrewanalytics

Access 'Homebrew' Formluae Analytics Data

## Description

The 'Homebrew Project' <brew.sh> has a myriad of "recipes" that make life easier for 'macOS' users by enabling them to (mostly) effortlessly install popular open source libraries, tools, utilities and applications. The project collectes anonymous metrics from users who have not opted-out of metrics collection and makes them available via a 'JSON' 'API'.

## What's Inside The Tin

The following functions are implemented:

For formulae info:

- `brew_formulae`:	Retrieve formulae metadata for all homebrew-core formulae

For info on "events": 

- `brew_analytics_events`:	Retrieve Analytics Events for Homebrew Formulae for a Given Category

These are just convenience and legacy API support wrappers for `brew_analytics_events()`

- `brew_build_error_events`:	Retrieve Analytics Events for Homebrew Formulae for a build-error events
- `brew_cask_install_events`:	Retrieve Analytics Events for Homebrew Formulae for a cask-install events
- `brew_install_events`:	Retrieve Analytics Events for Homebrew Formulae for a install events
- `brew_install_on_request_events`:	Retrieve Analytics Events for Homebrew Formulae for install-on-request events
- `brew_os_version_events`:	Retrieve Analytics Events for Homebrew Formulae for a OS events

## Installation

```{r eval=FALSE}
devtools::install_git("https://git.sr.ht.com/~hrbrmstr/homebrewanalytics")
# or
devtools::install_gitlab("hrbrmstr/homebrewanalytics")
# or
devtools::install_github("hrbrmstr/homebrewanalytics")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(homebrewanalytics)
library(tibble) # for printing

# current verison
packageVersion("homebrewanalytics")

```

### Formulae info

All:

```{r}
brew_formulae()
```

One:

```{r}
brew_formulae("curl")
```

Two:

```{r}
brew_formulae(c("curl", "wget"))
```

Errant name but still retrieves the rest:

```{r}
brew_formulae(c("curl", "wget", "doesnotexist"))
```

### Analytic Events

Retrieve formlua install events for the past 30, 90 or 365 days. We'll juse use the default:

```{r}
brew_install_events()
```

### Install On Request Events

Retrieve formlua install-on-request events for the past 30, 90 or 365 days

```{r}
brew_install_on_request_events()
```

### Build Error Events Events

Retrieve formlua build error events for the past 30

```{r}
brew_build_error_events()
```

```{r cloc}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that the 'homebrewanalytics' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.